\hypertarget{architecture-diagrams-plain-text}{%
\subsection{Architecture Diagrams (Plain Text)}\label{sec:00-Overview__architecture-diagrams:architecture-diagrams-plain-text}}

\hypertarget{system-context}{%
\subsubsection{System Context}\label{sec:00-Overview__architecture-diagrams:system-context}}

{[}Browser SPA{]} -\/-\/-\/-HTTPS-\/-\/-\/-\textgreater{} {[}Flask API /api{]}
{[}Flask API /api{]} -\/-\/-\/-\/-\textgreater{} {[}SQLite DB: User, History, Tool\_Counter, RefreshToken{]}
{[}Flask API /api{]} -\/-\/-\/-\/-\textgreater{} {[}External APIs: VirusTotal, Google Safe Browsing, IPGeolocation{]}

\hypertarget{tool-processing-flow}{%
\subsubsection{Tool Processing Flow}\label{sec:00-Overview__architecture-diagrams:tool-processing-flow}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Client obtains public RSA key from \texttt{/api/auth/public-key}.
\item
  Client encrypts credentials and calls \texttt{/api/auth/signup} or \texttt{/api/auth/login}.
\item
  Backend decrypts fields, validates credentials, and returns access/refresh tokens.
\item
  Client submits a URL or file to a tool endpoint with an access token.
\item
  Backend runs analysis, calculates risk score, then logs \texttt{History} and updates \texttt{Tool\_Counter}.
\item
  Client renders result, history, and counter metrics.
\end{enumerate}

\hypertarget{optional-dynamic-scan-link-analyzer}{%
\subsubsection{Optional Dynamic Scan (Link Analyzer)}\label{sec:00-Overview__architecture-diagrams:optional-dynamic-scan-link-analyzer}}

User-invoked deep/custom URL scans may use Playwright to collect dynamic page indicators. If Playwright is not installed or disabled, this step may fail and should be treated as optional or degraded.

\hypertarget{architecture-diagrams-text-description}{%
\subsection{Architecture Diagrams (Text Description)}\label{sec:00-Overview__architecture-diagrams:architecture-diagrams-text-description}}

\hypertarget{system-architecture}{%
\subsubsection{System Architecture}\label{sec:00-Overview__architecture-diagrams:system-architecture}}

User → Frontend SPA → DefendX Backend → Security Tools → Database

The frontend communicates with the backend exclusively via HTTPS. All authentication and authorization occur in the backend.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{tool-execution-flow}{%
\subsubsection{Tool Execution Flow}\label{sec:00-Overview__architecture-diagrams:tool-execution-flow}}

Request
→ JWT validation\\
→ Input validation\\
→ Tool execution\\
→ Risk scoring\\
→ History logging\\
→ Response

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{external-services-interaction}{%
\subsubsection{External Services Interaction}\label{sec:00-Overview__architecture-diagrams:external-services-interaction}}

The backend communicates with:

\begin{itemize}
\tightlist
\item
  VirusTotal
\item
  Google Safe Browsing
\item
  IP intelligence providers
\item
  Additional reputation or URL intelligence providers (deployment-dependent)
\end{itemize}

The frontend never communicates directly with these services.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{authentication-flow}{%
\subsubsection{Authentication Flow}\label{sec:00-Overview__architecture-diagrams:authentication-flow}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  User logs in
\item
  Backend issues JWT access and refresh tokens
\item
  Frontend uses access token for API calls
\item
  Backend validates token on each request
\end{enumerate}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{security-boundary}{%
\subsubsection{Security Boundary}\label{sec:00-Overview__architecture-diagrams:security-boundary}}

The backend is the sole trusted component. Compromise of the frontend does not imply compromise of the security engine.
