\hypertarget{future-work}{%
\subsection{Future Work}\label{sec:00-Overview__future-work:future-work}}

\begin{itemize}
\tightlist
\item
  Implement backend APIs for tools present in the frontend only (USB, PCAP, Audio, Behavioral Risk). Not evidenced in the reviewed codebase.
\item
  Add API rate limiting, request quotas, and abuse detection. Not evidenced in the reviewed codebase.
\item
  Provide production configuration (\texttt{prodconfig}) with secure database, secret management, and TLS guidance. Not evidenced in the reviewed codebase.
\item
  Harden token storage and client-side security (for example XSS protection strategy). Not evidenced in the reviewed codebase.
\item
  Expand audit logs with request metadata, tool inputs, and admin actions where appropriate. Not evidenced in the reviewed codebase.
\item
  Formalize Playwright sandboxing and resource limits for dynamic scans. Not evidenced in the reviewed codebase.
\end{itemize}

\hypertarget{stronger-ssrf-protections}{%
\subsubsection{Stronger SSRF Protections}\label{sec:00-Overview__future-work:stronger-ssrf-protections}}

Resolve hostnames and block private IP ranges.

\hypertarget{dynamic-file-analysis}{%
\subsubsection{Dynamic File Analysis}\label{sec:00-Overview__future-work:dynamic-file-analysis}}

Optional sandbox-based execution.

\hypertarget{enhanced-url-scoring}{%
\subsubsection{Enhanced URL Signal Scoring}\label{sec:00-Overview__future-work:enhanced-url-scoring}}

Expanded URL signal normalization and weighting.

\hypertarget{expanded-reputation-coverage}{%
\subsubsection{Expanded Reputation Coverage}\label{sec:00-Overview__future-work:expanded-reputation-coverage}}

Additional defensive reputation data sources for URL and file analysis.

\hypertarget{configurable-risk-scoring}{%
\subsubsection{Configurable Risk Scoring}\label{sec:00-Overview__future-work:configurable-risk-scoring}}

Externalized scoring weights.

\hypertarget{native-metrics}{%
\subsubsection{Native Metrics}\label{sec:00-Overview__future-work:native-metrics}}

Tool latency and error metrics.

\hypertarget{api-versioning}{%
\subsubsection{API Versioning}\label{sec:00-Overview__future-work:api-versioning}}

Introduce versioned endpoints.
