\hypertarget{security-controls-mapping}{%
\subsection{Security Controls Mapping}\label{sec:00-Overview__security-controls-mapping:security-controls-mapping}}

This is a control-to-implementation map based on the current repository. Items not evidenced in code are marked TBD.

\hypertarget{access-control}{%
\subsubsection{Access Control}\label{sec:00-Overview__security-controls-mapping:access-control}}

\begin{itemize}
\tightlist
\item
  Control: Role-based access enforcement for admin operations.
\item
  Evidence: \texttt{backend/app/user.py} uses \texttt{require\_admin()} and role checks; \texttt{backend/app/\_\_init\_\_.py} defines \texttt{require\_admin()}.
\item
  Status: Implemented.
\end{itemize}

\hypertarget{authentication-and-session-management}{%
\subsubsection{Authentication and Session Management}\label{sec:00-Overview__security-controls-mapping:authentication-and-session-management}}

\begin{itemize}
\tightlist
\item
  Control: Password hashing and JWT-based session tokens with refresh rotation.
\item
  Evidence: \texttt{backend/app/auth.py}, \texttt{backend/app/models.py} (\texttt{RefreshToken}).
\item
  Status: Implemented.
\end{itemize}

\hypertarget{credential-transport-security}{%
\subsubsection{Credential Transport Security}\label{sec:00-Overview__security-controls-mapping:credential-transport-security}}

\begin{itemize}
\tightlist
\item
  Control: RSA encryption for credential fields in the client, decryption server-side.
\item
  Evidence: \texttt{frontend/src/api/encryption.js}, \texttt{backend/app/security.py}.
\item
  Status: Implemented.
\end{itemize}

\hypertarget{audit-logging}{%
\subsubsection{Audit Logging}\label{sec:00-Overview__security-controls-mapping:audit-logging}}

\begin{itemize}
\tightlist
\item
  Control: Tool usage history with timestamps and user metadata.
\item
  Evidence: \texttt{backend/app/history.py}, \texttt{backend/app/models.py}.
\item
  Status: Implemented.
\end{itemize}

\hypertarget{operational-metrics}{%
\subsubsection{Operational Metrics}\label{sec:00-Overview__security-controls-mapping:operational-metrics}}

\begin{itemize}
\tightlist
\item
  Control: Per-user counters for tool usage.
\item
  Evidence: \texttt{backend/app/toolcount.py}, \texttt{backend/app/models.py}.
\item
  Status: Implemented.
\end{itemize}

\hypertarget{input-validation-and-hardening}{%
\subsubsection{Input Validation and Hardening}\label{sec:00-Overview__security-controls-mapping:input-validation-and-hardening}}

\begin{itemize}
\tightlist
\item
  Control: Request validation models and URL target filtering.
\item
  Evidence: Flask-RESTX models in \texttt{backend/Tools/link\_analyzer/route/schemas.py}, \texttt{is\_public\_http} in \texttt{backend/Tools/link\_analyzer/route/route.py}.
\item
  Status: Implemented.
\end{itemize}

\hypertarget{path-traversal-protection}{%
\subsubsection{Path Traversal Protection}\label{sec:00-Overview__security-controls-mapping:path-traversal-protection}}

\begin{itemize}
\tightlist
\item
  Control: Block traversal markers and forbidden file extensions.
\item
  Evidence: \texttt{backend/app/\_\_init\_\_.py} request filtering.
\item
  Status: Implemented.
\end{itemize}

\hypertarget{secrets-management}{%
\subsubsection{Secrets Management}\label{sec:00-Overview__security-controls-mapping:secrets-management}}

\begin{itemize}
\tightlist
\item
  Control: Environment-based secrets and API keys.
\item
  Evidence: \texttt{backend/config.py} uses \texttt{decouple} config variables.
\item
  Status: Partially implemented; rotation and vault integration are TBD.
\end{itemize}

\hypertarget{rate-limiting-and-abuse-prevention}{%
\subsubsection{Rate Limiting and Abuse Prevention}\label{sec:00-Overview__security-controls-mapping:rate-limiting-and-abuse-prevention}}

\begin{itemize}
\tightlist
\item
  Control: API rate limiting and quotas.
\item
  Evidence: Not found.
\item
  Status: TBD (verify in code).
\end{itemize}

\begin{longtable}[]{@{}ll@{}}
\toprule
Area & Control \\
\midrule
\endhead
Authentication & JWT access \& refresh tokens \\
Authorization & Role-based access control \\
Input Validation & Server-side validation \\
Sensitive Data & Hash-only processing \\
URL Safety & SSRF target filtering and allow/deny rules \\
File Safety & Static analysis only \\
Auditability & History logging \\
Abuse Prevention & Tool usage counters \\
Privacy & Minimal retention \\
Failure Safety & Risk-increasing failures \\
\bottomrule
\end{longtable}
