\hypertarget{operations-and-monitoring}{%
\subsection{Operations and Monitoring}\label{sec:05-Deployment__operations-and-monitoring:operations-and-monitoring}}

\hypertarget{observability}{%
\subsubsection{Observability}\label{sec:05-Deployment__operations-and-monitoring:observability}}

\begin{itemize}
\tightlist
\item
  No explicit logging or metrics framework is configured in code (TBD (verify in code)).
\item
  Consider adding structured logging and request tracing for API endpoints.
\end{itemize}

\hypertarget{health-and-status}{%
\subsubsection{Health and Status}\label{sec:05-Deployment__operations-and-monitoring:health-and-status}}

\begin{itemize}
\tightlist
\item
  \texttt{GET\ /api/user/hello} is a lightweight health check.
\item
  \texttt{GET\ /api/auth/public-key} can also validate cryptographic readiness.
\end{itemize}

\hypertarget{alerting}{%
\subsubsection{Alerting}\label{sec:05-Deployment__operations-and-monitoring:alerting}}

\begin{itemize}
\tightlist
\item
  No alerting rules are configured in code (TBD (verify in code)).
\end{itemize}

\hypertarget{backups}{%
\subsubsection{Backups}\label{sec:05-Deployment__operations-and-monitoring:backups}}

\begin{itemize}
\tightlist
\item
  Backup strategy for database is not defined in code (TBD (verify in code)).
\end{itemize}

\hypertarget{incident-response}{%
\subsubsection{Incident Response}\label{sec:05-Deployment__operations-and-monitoring:incident-response}}

\begin{itemize}
\tightlist
\item
  No incident response automation is defined in code (TBD (verify in code)).
\end{itemize}

\hypertarget{purpose}{%
\subsubsection{Purpose}\label{sec:05-Deployment__operations-and-monitoring:purpose}}

This document describes how to \textbf{operate, monitor, and maintain} DefendX once deployed.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{logging}{%
\subsubsection{Logging}\label{sec:05-Deployment__operations-and-monitoring:logging}}

DefendX should log:

\begin{itemize}
\tightlist
\item
  Authentication events
\item
  Tool execution events
\item
  Errors and failures
\end{itemize}

Logs must not contain:

\begin{itemize}
\tightlist
\item
  Plaintext credentials
\item
  Tokens
\item
  File contents
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{monitoring}{%
\subsubsection{Monitoring}\label{sec:05-Deployment__operations-and-monitoring:monitoring}}

Recommended monitoring signals include:

\begin{itemize}
\tightlist
\item
  Tool execution counts
\item
  Error rates per tool
\item
  External API failure rates
\item
  Authentication failures
\end{itemize}

Monitoring supports:

\begin{itemize}
\tightlist
\item
  Incident response
\item
  Capacity planning
\item
  Abuse detection
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{alerting-1}{%
\subsubsection{Alerting}\label{sec:05-Deployment__operations-and-monitoring:alerting-1}}

Alerts should be configured for:

\begin{itemize}
\tightlist
\item
  Sudden spikes in tool usage
\item
  Repeated authentication failures
\item
  External intelligence API outages
\item
  Database errors or unavailability
\end{itemize}

Alerts should be actionable and not overly noisy.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{failure-handling}{%
\subsubsection{Failure Handling}\label{sec:05-Deployment__operations-and-monitoring:failure-handling}}

DefendX is designed to fail safely:

\begin{itemize}
\tightlist
\item
  External API failures increase risk
\item
  Partial results returned explicitly
\item
  Observability failures do not block analysis
\end{itemize}

Operators should investigate repeated partial failures.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{maintenance-activities}{%
\subsubsection{Maintenance Activities}\label{sec:05-Deployment__operations-and-monitoring:maintenance-activities}}

Regular maintenance should include:

\begin{itemize}
\tightlist
\item
  Reviewing audit logs
\item
  Rotating secrets
\item
  Updating dependencies
\item
  Reviewing risk scoring assumptions
\item
  Cleaning up old data if retention policies exist
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{incident-response-1}{%
\subsubsection{Incident Response}\label{sec:05-Deployment__operations-and-monitoring:incident-response-1}}

In case of suspected compromise:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Review audit history
\item
  Rotate affected secrets
\item
  Revoke tokens if necessary
\item
  Investigate anomalous usage
\item
  Document findings and remediation
\end{enumerate}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{operational-philosophy}{%
\subsubsection{Operational Philosophy}\label{sec:05-Deployment__operations-and-monitoring:operational-philosophy}}

DefendX should be operated as a \textbf{security system}, not just an application.

Transparency, caution, and auditability are more important than silent availability.
