\hypertarget{project-overview}{%
\subsection{Project Overview}\label{sec:00-Overview__project-overview:project-overview}}

DefendX is a web-based security analysis platform focused on protecting users from social engineering attacks through a Flask API and a React/Vite dashboard. The system provides the URL Risk Analysis Tool (Link Analyzer), file download scanning, and operational logging.

\hypertarget{purpose}{%
\subsubsection{Purpose}\label{sec:00-Overview__project-overview:purpose}}

DefendX is a security analysis platform designed to identify and assess risks introduced through explicit user inputs, including:

\begin{itemize}
\tightlist
\item
  URLs
\item
  Files
\end{itemize}

The platform provides explainable risk assessments, auditability, and actionable guidance without executing untrusted content.
All analysis tools in DefendX operate exclusively on explicit user input and do not perform background monitoring, credential harvesting, or passive data collection.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{core-objectives}{%
\subsubsection{Core Objectives}\label{sec:00-Overview__project-overview:core-objectives}}

DefendX is designed to:

\begin{itemize}
\tightlist
\item
  Detect common and advanced threat indicators
\item
  Provide transparent and explainable risk scores
\item
  Preserve user privacy
\item
  Maintain strong auditability
\item
  Operate safely under partial failure
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{what-defendx-is}{%
\subsubsection{What DefendX Is}\label{sec:00-Overview__project-overview:what-defendx-is}}

\begin{itemize}
\tightlist
\item
  A centralized security analysis engine
\item
  A backend-driven trust decision system
\item
  A modular tool-based architecture
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{what-defendx-is-not}{%
\subsubsection{What DefendX Is Not}\label{sec:00-Overview__project-overview:what-defendx-is-not}}

\begin{itemize}
\tightlist
\item
  An antivirus engine
\item
  A sandbox execution platform (by default)
\item
  A replacement for endpoint security
\item
  A real-time intrusion prevention system
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{security-philosophy}{%
\subsubsection{Security Philosophy}\label{sec:00-Overview__project-overview:security-philosophy}}

DefendX follows these principles:

\begin{itemize}
\tightlist
\item
  Assume all external input is malicious
\item
  Treat the frontend as untrusted
\item
  Prefer false positives over false negatives
\item
  Fail safely and visibly
\item
  Avoid black-box decisions
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{high-level-capabilities}{%
\subsubsection{High-Level Capabilities}\label{sec:00-Overview__project-overview:high-level-capabilities}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Capability & Description \\
\midrule
\endhead
URL Risk Analysis & URL reputation, redirects, SSL, and optional dynamic checks \\
File Analysis & Static file inspection and reputation \\
\bottomrule
\end{longtable}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{trust-model}{%
\subsubsection{Trust Model}\label{sec:00-Overview__project-overview:trust-model}}

\begin{itemize}
\tightlist
\item
  Backend: trusted
\item
  Frontend: untrusted
\item
  External services: untrusted but useful
\item
  User input: hostile by default
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{system-boundary}{%
\subsubsection{System Boundary}\label{sec:00-Overview__project-overview:system-boundary}}

DefendX makes security decisions server-side and returns results to clients. It does not execute untrusted content or take autonomous remediation actions.

\hypertarget{scope}{%
\subsubsection{Scope}\label{sec:00-Overview__project-overview:scope}}

\begin{itemize}
\tightlist
\item
  Backend API serving authenticated tool endpoints under \texttt{/api}.
\item
  Frontend SPA that drives authenticated workflows and reports.
\item
  User-invoked URL and file analysis workflows through authenticated API requests.
\end{itemize}

\hypertarget{primary-data-flows}{%
\subsubsection{Primary Data Flows}\label{sec:00-Overview__project-overview:primary-data-flows}}

\begin{itemize}
\tightlist
\item
  Users authenticate via \texttt{/api/auth/login} with RSA-encrypted credential fields.
\item
  Backend issues JWT access and refresh tokens and stores refresh token state in the database.
\item
  Tool endpoints process user inputs, compute risk scores, and log usage in \texttt{History} and \texttt{Tool\_Counter} tables.
\item
  Frontend displays findings, status, and usage history from the API.
\end{itemize}

\hypertarget{data-classes}{%
\subsubsection{Data Classes}\label{sec:00-Overview__project-overview:data-classes}}

\begin{itemize}
\tightlist
\item
  Account data: \texttt{User} (username, email, role, suspended flags).
\item
  Auth data: JWT access and refresh tokens, refresh token server-side records.
\item
  Tool data: user-provided URLs, file metadata, and tool outputs.
\item
  Logs: tool usage history and per-user counters.
\end{itemize}

\hypertarget{external-dependencies}{%
\subsubsection{External Dependencies}\label{sec:00-Overview__project-overview:external-dependencies}}

\begin{itemize}
\tightlist
\item
  VirusTotal, Google Safe Browsing, and IPGeolocation (API-backed checks).
\item
  Playwright for optional dynamic link analysis.
\end{itemize}

\hypertarget{out-of-scope}{%
\subsubsection{Out of Scope}\label{sec:00-Overview__project-overview:out-of-scope}}

\begin{itemize}
\tightlist
\item
  Backend APIs for tools present only in frontend routes (USB, PCAP, Audio, User Behavior) are not confirmed in this repository. See \texttt{00-Overview/known-limitations.md}.
\end{itemize}
