\hypertarget{executive-security-summary}{%
\subsection{Executive Security Summary}\label{sec:99-Executive__executive-security-summary:executive-security-summary}}

\hypertarget{overview}{%
\subsubsection{Overview}\label{sec:99-Executive__executive-security-summary:overview}}

DefendX provides a multi-tool defensive platform for social engineering detection with authenticated API access, structured tool outputs, and operational logging. The system includes JWT authentication with refresh rotation, RSA-based credential encryption, and API-level request hardening for static assets.

\hypertarget{security-strengths}{%
\subsubsection{Security Strengths}\label{sec:99-Executive__executive-security-summary:security-strengths}}

\begin{itemize}
\tightlist
\item
  JWT access + refresh tokens with server-side refresh revocation.
\item
  RSA encryption of credentials in the client, decrypted server-side.
\item
  Per-tool audit logging and usage counters.
\item
  URL target validation to avoid private/loopback scans.
\item
  Path traversal protections for static file serving.
\end{itemize}

\hypertarget{key-risks}{%
\subsubsection{Key Risks}\label{sec:99-Executive__executive-security-summary:key-risks}}

\begin{itemize}
\tightlist
\item
  Tokens stored in \texttt{localStorage} (XSS exposure risk).
\item
  No explicit rate limiting or abuse controls found in code.
\item
  Production configuration is not fully defined (prod DB and secrets management TBD).
\item
  Several tool routes are present in frontend without confirmed backend endpoints.
\end{itemize}

\hypertarget{recommended-priorities}{%
\subsubsection{Recommended Priorities}\label{sec:99-Executive__executive-security-summary:recommended-priorities}}

\begin{itemize}
\tightlist
\item
  Implement rate limiting and abuse detection.
\item
  Align frontend tool routes with backend APIs.
\item
  Formalize production config and database controls.
\item
  Review Playwright sandboxing before enabling deep scans at scale.
\end{itemize}
