\hypertarget{security-whitepaper}{%
\subsection{Security Whitepaper}\label{sec:99-Executive__security-whitepaper:security-whitepaper}}

\hypertarget{abstract}{%
\subsubsection{Abstract}\label{sec:99-Executive__security-whitepaper:abstract}}

DefendX is a multi-tool cybersecurity platform designed to analyze social engineering threats through a unified API and dashboard. It integrates static and dynamic analysis methods, reputation checks, and structured scoring to support defensive decision-making.

\hypertarget{system-architecture}{%
\subsubsection{System Architecture}\label{sec:99-Executive__security-whitepaper:system-architecture}}

\begin{itemize}
\tightlist
\item
  Flask API with REST namespaces under \texttt{/api}.
\item
  React/Vite SPA for interactive tool workflows.
\item
  SQLAlchemy models for identity, logging, and token state.
\item
  Optional Celery workers for asynchronous tasks.
\end{itemize}

\hypertarget{security-design}{%
\subsubsection{Security Design}\label{sec:99-Executive__security-whitepaper:security-design}}

\begin{itemize}
\tightlist
\item
  Credential encryption: RSA public key retrieval and client-side encryption.
\item
  Authentication: JWT access tokens and rotated refresh tokens stored server-side.
\item
  Authorization: Admin role enforced on privileged endpoints.
\item
  Request hardening: traversal and file marker blocking for static assets.
\item
  SSRF mitigation: Link Analyzer validates public HTTP targets.
\end{itemize}

\hypertarget{tool-capabilities}{%
\subsubsection{Tool Capabilities}\label{sec:99-Executive__security-whitepaper:tool-capabilities}}

\begin{itemize}
\tightlist
\item
  Link Analyzer: reputation checks, SSL inspection, redirect analysis, and optional dynamic analysis.
\item
  File Download Checker: static analysis and VirusTotal hash reputation.
\end{itemize}

\hypertarget{data-handling}{%
\subsubsection{Data Handling}\label{sec:99-Executive__security-whitepaper:data-handling}}

\begin{itemize}
\tightlist
\item
  Access tokens stored client-side; refresh tokens rotated and tracked server-side.
\end{itemize}

\hypertarget{limitations}{%
\subsubsection{Limitations}\label{sec:99-Executive__security-whitepaper:limitations}}

\begin{itemize}
\tightlist
\item
  No explicit rate limiting or abuse controls in code.
\item
  Production configuration and storage hardening are TBD.
\item
  Some frontend tool pages do not have verified backend support.
\end{itemize}

\hypertarget{conclusion}{%
\subsubsection{Conclusion}\label{sec:99-Executive__security-whitepaper:conclusion}}

DefendX provides a strong security foundation for social-engineering detection, but it requires additional production hardening, monitoring, and feature alignment to meet enterprise requirements.
