\hypertarget{audit-readiness-checklist}{%
\subsection{Audit Readiness Checklist}\label{sec:99-Executive__audit-readiness-checklist:audit-readiness-checklist}}

\hypertarget{identity-and-access}{%
\subsubsection{Identity and Access}\label{sec:99-Executive__audit-readiness-checklist:identity-and-access}}

\begin{itemize}
\tightlist
\item
  JWT access and refresh tokens implemented.
\item
  Admin role enforcement via \texttt{require\_admin()}.
\item
  Account lockout after three failed login attempts.
\end{itemize}

\hypertarget{data-protection}{%
\subsubsection{Data Protection}\label{sec:99-Executive__audit-readiness-checklist:data-protection}}

\begin{itemize}
\tightlist
\item
  RSA encryption of credential fields in the client.
\item
  Backend decryption and secure key management (file-based or env-based).
\end{itemize}

\hypertarget{logging-and-monitoring}{%
\subsubsection{Logging and Monitoring}\label{sec:99-Executive__audit-readiness-checklist:logging-and-monitoring}}

\begin{itemize}
\tightlist
\item
  Tool usage logs captured in \texttt{History}.
\item
  Usage counters tracked in \texttt{Tool\_Counter}.
\item
  No centralized logging framework configured (TBD (verify in code)).
\end{itemize}

\hypertarget{secure-development}{%
\subsubsection{Secure Development}\label{sec:99-Executive__audit-readiness-checklist:secure-development}}

\begin{itemize}
\tightlist
\item
  Request hardening for static file paths.
\item
  Input validation via Flask-RESTX models for tool endpoints.
\end{itemize}

\hypertarget{infrastructure}{%
\subsubsection{Infrastructure}\label{sec:99-Executive__audit-readiness-checklist:infrastructure}}

\begin{itemize}
\tightlist
\item
  SQLite used for dev/test. Production DB config TBD.
\item
  Celery integration present; broker/backends must be configured.
\end{itemize}

\hypertarget{evidence-locations}{%
\subsubsection{Evidence Locations}\label{sec:99-Executive__audit-readiness-checklist:evidence-locations}}

\begin{itemize}
\tightlist
\item
  \texttt{backend/app/auth.py}
\item
  \texttt{backend/app/security.py}
\item
  \texttt{backend/app/history.py}
\item
  \texttt{backend/app/toolcount.py}
\item
  \texttt{backend/app/\_\_init\_\_.py}
\item
  \texttt{backend/Tools/*}
\end{itemize}
